FHJ: A Formal Model for Resolving Unintended Conflicts in Multiple Inheritance

### 2017-06-15 Aplas17/sections/Overview.tex
overview

\begin{figure*}[t]
\centering
\includegraphics[height=2cm]{pics/DrawableLoggingDeck.pdf}
\caption{DrawableLoggingDeck UML}\label{fig:subtyping}
\end{figure*}
\bruno{I've said this several times in the past: please use proper UML
notation! The UML arrows are not right.}
\bruno{This figure is never referred to in the text! You need to talk 
about the figure in the text.}

@@

\subsection{Problem 2: Dynamic Dispatch for Code Reuse}
On the other hand, we also need dynamic dispatch as it is essential and widely used in object-oriented programming.
C++ has the flexibility for choosing either way of dispatch by the \kwvirtual{} keyword.
Unfortunately, this approach is still unsatisfactory regarding code reuse. For instance, here we redefine \lstinline|Deck| to support
both \lstinline|draw()| and another operation called \lstinline|shuffleAndDraw()|:
\vspace{3pt}\begin{lstlisting}
interface Deck {
  void draw() {...}
  void shuffleAndDraw() {
    shuffle();
    draw();
  }
  ...
}
\end{lstlisting}\vspace{3pt}
\lstinline|shuffleAndDraw()| is a representative method that invokes \lstinline|draw()| in its definition. In principle, we want
that invocation to use dynamic dispatch, because a programmer may define a subtype of \lstinline|Deck|, and override \lstinline|draw()|:
\vspace{3pt}\begin{lstlisting}
interface LoggingDeck {
  void draw() { // overriding
    Stack<Card> cards = this.getStack();
    if (!cards.isEmpty()) {
      Card card = cards.pop();
      println("The card is: " + card.toString());
      ...
    } else {
      println("Empty deck.");
    }
  }
}
\end{lstlisting}\vspace{3pt}
Usually we want to reuse the code of \lstinline|shuffleAndDraw()| during inheritance, hence dynamic dispatch is necessary, otherwise
programmers have to override all the other methods that invoke \lstinline|draw()|. However, as seen before, dynamic dispatch can cause
ambiguity if we have:
\vspace{3pt}\begin{lstlisting}
interface DrawableLoggingDeck extends Drawable, LoggingDeck {...}

>>>>

\bruno{I've said this several times in the past: please use proper UML
notation! The UML arrows are not right.}
\bruno{This figure is never referred to in the text! You need to talk 
about the figure in the text.}

@@

\subsection{Problem 2: Dynamic Dispatch for Code Reuse}
\begin{figure*}[t]
\centering
\includegraphics[height=2cm]{pics/DrawableLoggingDeck.pdf}
\caption{DrawableLoggingDeck UML}\label{fig:drawableloggingdeck}
\end{figure*}

On the other hand, we also need dynamic dispatch as it is essential and widely used in object-oriented programming.
C++ has the flexibility for choosing either way of dispatch by the \kwvirtual{} keyword.
Unfortunately, this approach is still unsatisfactory regarding code reuse. For instance in Figure~\ref{fig:drawableloggingdeck}, 
we redefine \lstinline|Deck| to support
both \lstinline|draw()| and another operation called \lstinline|shuffleAndDraw()|:
\vspace{3pt}\begin{lstlisting}
interface Deck {
  void draw() {...}
  void shuffleAndDraw() {
    shuffle();
    draw();
  }
  ...
}
\end{lstlisting}\vspace{3pt}
\lstinline|shuffleAndDraw()| is a representative method that invokes \lstinline|draw()| in its definition. In principle, we want
that invocation to use dynamic dispatch, because a programmer may define a subtype of \lstinline|Deck|, and override \lstinline|draw()|:
\vspace{3pt}\begin{lstlisting}
interface LoggingDeck {
  void draw() { // overriding
    Stack<Card> cards = this.getStack();
    if (!cards.isEmpty()) {
      Card card = cards.pop();
      println("The card is: " + card.toString());
      ...
    } else {
      println("Empty deck.");
    }
  }
}
\end{lstlisting}\vspace{3pt}
Usually we want to reuse the code of \lstinline|shuffleAndDraw()| during inheritance, hence dynamic dispatch is necessary, otherwise
programmers have to override all the other methods that invoke \lstinline|draw()|. However, as seen before, dynamic dispatch can cause
ambiguity if we have:
\vspace{3pt}\begin{lstlisting}
interface DrawableLoggingDeck extends Drawable, LoggingDeck {...}
